### 2019-04-29 report/chapter03.Rnw
Presentation upload

@

\section{Meta-analysis}
The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect. The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences. This led to somewhat more than 400,000 significance test results. Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).

\begin{figure}
<<echo=FALSE, warning=FALSE>>=
data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
@
\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
\label{study.significance.overtime}
\end{figure}

It is possible to analyse all studies with one or more replica by meta-analysis. There are different meta-analys methods that can be applied. While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate. The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.

\vspace{0mm}
In the following, the study results are combined with the results of their corresponding meta-analysis. Thus, every study that has one or more replicate was analysed by meta-analysis. In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.

\vspace{0mm}
In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown. The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure. One can see the overall fraction of rejected null-hypotheses of no treatment effect.

@@

One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, i.e. non-pooled effect, and non-significant primary treatment effect. This can be seen in Figure \ref{primary.secondary.significance.sep.sig}. One can see that primary significance and non-significance is often overruled when performing a meta-analysis.

@@

The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis. Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution. The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested. This is shown in Figure \ref{primary.secondary.significance.sep.sig}.

\begin{figure}
<<echo=FALSE, warning=FALSE>>=
grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
@
\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate. The fractions have been calculated
by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
\label{primary.secondary.significance.sep.sig}
\end{figure}

\section{Small study effects}
One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect. If this is not given, one often speaks of publication bias. In fact, there can also be other reasons for this (see discussion section). A more appropriate term for the phenomenon is small study effect. If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.

\vspace{0mm}
To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}. In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.

\vspace{0mm}
A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off. With increasing sample size, there are fewer results, therefore, the variation between medians increases. All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation. Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.

\begin{figure}
<<echo=FALSE>>=
data %>% filter(total1 + total2 > 10 & total1 + total2 < 200) %>% 
  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
  group_by(sample.size) %>% 
  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
  ggplot(aes(x = sample.size, y = median.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
@
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
\label{effect.samplesize}
\end{figure}

The median absolute normalized effect size can be visualized for the different outcome measures separately. Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences. Instead of normalizing the effects (i.e. subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.

\begin{figure}
<<echo=FALSE>>=
levels(data$outcome.measure.new) <- c("Mean Difference", "Std. Mean Difference", "Odds Ratio", "Risk Ratio")

data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
  filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
           outcome.measure.new == "Std. Mean Difference") %>% 
  group_by(outcome.measure.new) %>% 
  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
  group_by(sample.size, outcome.measure.new) %>% 
  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new, scales = "free") + 
  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
@
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
\label{effect.samplesize.separated}
\end{figure}

% It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g. mean publication year (of studies included in the meta-analysis). 0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection. To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$). The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis. As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time. 
% 
% \begin{figure}
% <<echo=FALSE>>=
% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
%   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
% @
% \caption{Proportion of significant treatment effect estimates over time (mean publication year).}
% \label{effect.samplesize}
% \end{figure}
%

@@

p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>%  
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) +
  annotate("text", x = test.bin$test.type, y = 1000, 
           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
           color = "white")

test.sig.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                              schwarzer.test = mean(schwarzer.test),
                                                              rucker.test = mean(rucker.test),
                                                              harbord.test = mean(harbord.test),
                                                              peter.test = mean(peter.test))
test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")

p1 <- meta.bin %>% ungroup() %>% 
select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
  annotate("text", x = test.sig.bin$test.type, y = 1750, 
           label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
           color = "white")

@@

@@

@@

@@

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = \Sexpr{n.cont})
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).

@@

The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes. This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.

\begin{figure}
<<echo=FALSE, warning=FALSE>>=
grid.arrange(p3, p4, ncol = 2)
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont.sep}
\end{figure}

\begin{figure}
<<echo=FALSE, warning=FALSE>>=
grid.arrange(p1, p2, ncol = 2)
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin.sep}
\end{figure}

Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses). The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}. The Figure suggests that the frequency of publication bias remains constant over time. The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent. The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).

@@

@@

>>>>

p.secondary.over.meansig <- mly %>% filter(NA.sig.type != 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
  geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
@

\section{Meta-analysis}
The data at hand is composed of over 400,000 results with balanced sample size $n > 24$. The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.

%Significance over time? Chunck 1

It is possible to analyse all results that are not unique in their comparison, outcome and subgroup in the dataset by meta-analysis. So each study that has been repeated with respect to experimental setup is included. There are different meta-analys methods that can be applied, here, fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis using the Hartung-Knapp method are used.

\vspace{0mm}
In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e. if studies were not unique in the dataset with respect to their experimental setup). The significant of the treatment effect in a single result is then compared to the significance of the pooled treatment effect. 
In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown. The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure. The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.

@@

One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, and non-significant primary treatment effect, as done in Figure \ref{primary.secondary.significance.sep.sig}. It can be seen that primary significance and non-significance is often overruled when performing a meta-analysis.

@@

The amount of significant heterogeneity in the results used by the meta-analyses is \Sexpr{length(which(mly$sig.Q == 0))} and corresponds to \Sexpr{(length(which(mly$sig.Q == 0))/ dim(mly)[1])*100}\% of the total number of meta-analyses.

%Comparison of significance separated for significant Q? Chunck 2

%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5

\section{Small study effects}

<<echo=FALSE>>=
p.samplesize.effect <- data %>% filter(total1 + total2 > 10 & total1 + total2 < 200) %>% 
  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
  group_by(sample.size) %>% 
  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
  ggplot(aes(x = sample.size, y = median.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")

#levels(data$outcome.measure.new) <- c("Mean Difference", "Std. Mean Difference", "Odds Ratio", "Risk Ratio")

p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
  filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
           outcome.measure.new == "Std. Mean Difference") %>% 
  group_by(outcome.measure.new) %>% 
  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
  group_by(sample.size, outcome.measure.new) %>% 
  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new, scales = "free") + 
  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
@

To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}). 
%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.

\vspace{0mm}
A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off. With increasing sample size, there are fewer results, therefore, the variation between medians increases. 
All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation. Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.

\begin{figure}
<<echo=FALSE>>=
plot(p.samplesize.effect)
@
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
\label{effect.samplesize}
\end{figure}

The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}). The plot confirms the trend of median effect size decrease towards lower sample size (e.g. for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants). Instead of normalizing the effects 
%(i.e. subtracting mean and dividing through the standard deviation) 
for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.

\begin{figure}
<<echo=FALSE>>=
plot(p.samplesize.effect.sep)
@
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
\label{effect.samplesize.separated}
\end{figure}

%Show absolute effect size depending on scaled time? Chunck 3

@@

p.bin <- meta.bin %>% ungroup() %>% 
  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>%  
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) +
  annotate("text", x = test.bin$test.type, y = 1000, 
           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
           color = "white")

test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                              schwarzer.test = mean(schwarzer.test),
                                                              rucker.test = mean(rucker.test),
                                                              harbord.test = mean(harbord.test),
                                                              peter.test = mean(peter.test))
test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")

p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
  annotate("text", x = test.sig.bin$test.type, y = 1750, 
           label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
           color = "white")

@@

range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)

@@

range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)

@@

# Significance after correction plots, separated for meta-analyses with significant publication bias test.
change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with significant small study effect")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>%   mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with non-significant small study effect")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

@@

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = \Sexpr{n.cont})
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}). The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.

@@

There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not. Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by \Sexpr{range.pb.difference.bin[2]} (the minimal increase is \Sexpr{range.pb.difference.bin[1]} for Schwarzer's Test).

%Show plots of significant meta-analyses separated? Chunck 4

Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses). The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}. The Figure suggests that the frequency of publication bias remains constant over time. The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent. The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).

@@

Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section. Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses. The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc. are shown in Figure \ref{significance.change.fixed.sep}. Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.

\begin{figure}
<<echo=FALSE, warning=FALSE>>=
grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
@
\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
\label{significance.change.random}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}. The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800). 
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
% @
% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
% \label{study.significance.overtime}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis. Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution. The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested. This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
% @
% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate. The fractions have been calculated
% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
% \label{primary.secondary.significance.sep.sig}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 4
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes. This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% grid.arrange(p3, p4, ncol = 2)
% @
% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
% \label{bias.results.cont.sep}
% \end{figure}
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% grid.arrange(p1, p2, ncol = 2)
% @
% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
% \label{bias.results.bin.sep}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% #Proportion of significant pooled estimates based on proportion of single pooled estimates
% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
% 
% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
%   geom_density(na.rm = T, position = "fill") + 
%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
% 
% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
%   geom_histogram(position = "fill")
% 
% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
%   geom_histogram()

% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% plot(p.secondary.over.meansig)
% @
% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
% \label{secondary.significance.over.meansig}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chunck 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
